\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{grey}

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{hyperref}
\usepackage[scale=0.75]{geometry}
\usepackage{color}

\firstname{Alexander}
\familyname{Chernetsky}
\address{8A, Vodolajskogo str. Apt 48}{Minsk, Belarus 220056}
\mobile{+375~(29)~3683767}
\email{alexander.chernetsky@gmail.com}
\extrainfo{Birthday date: 10 Jun 1991}

\begin{document}

\makecvtitle

\section{Summary}

Team Lead / Senior Software Engineer with broad experience (8+ years) in software development.

Highly motivated and self-driven person with strong soft and problem solving skills.

The most used technical skills include Python2/3 (Django, Asyncio, Aiohttp), JavaScript (React, Backbone, and other frameworks), Golang.

\section{Experience}

\subsection{Kyriba (\url{https://www.kyriba.by/}), Minsk}
\cventry{February 2019 - Present}{Team Lead / Senior Software Engineer}{}{}{}{For the Format project, I have been taking the role of a team lead. I am responsible for:
\begin{itemize}
  \item requirements analysis;
  \item writing SDD for team developers and lead some key features of projects;
  \item low-level planning and estimation;
  \item communication and solving issues among other teams;
  \item maintaining and implementing new parts;
  \item supporting of legacy code;
  \item providing feedback, mentoring, team development, interviewing, onboarding and so on;
\end{itemize}}
\cvline{tools}{\emph{Windows 10, Python 2, Robot Framework, MongoDB, Jenkins.}}

\subsection{Wargaming (\url{http://wargaming.net}), Minsk}
\cventry{Septermber 2015 - October 2018}{Full stack web developer of client in game browser solutions}{}{}{}{Development single-page applications for World of Tanks and World of Warships client browser (cef). I developed the following key parts of the services:
\begin{itemize}
  \item authentication worker based on wargaming internal system;
  \item write SDD for team developers and lead some key features of projects;
  \item react components collection and helpers for cef applications in World of Tanks Client;
\end{itemize}
I communicated effectively with a large number of departments, such as QA, Pre-production, Release managers, Localizers, Business analysts.
I also had the mentoring experience.}
\cvline{tools}{\emph{Linux, Python 2/3 (Aiohttp, Django), RabbitMQ, Redis, React, PostgreSQL, TeamCity}}

\cventry{}{Full stack web developer of clan portal}{}{}{}{Support of legacy code of \href{http://wargaming.net/clans}{Clan portal}, bug-fixing and implementation of new features.}
\cvline{tools}{\emph{Linux, Python (Django, Wagtail), RabbitMQ, Backbone, PostgreSQL, TeamCity}}

\subsection{Gurtsoft (\url{http://gurtam.com}), Minsk}
\cventry{August 2012 - August 2015}{Developer of Gurtam GIS services}{}{}{}{Support of legacy code of GIS service such as Gurtam Maps, geocoding and reverse geocoding, also bug-fixing and implementation of new features.}
\cvline{tools}{\emph{Linux, C++, gcc, GNU make, Berkeley DB.}}

\cventry{}{Key developer of Gurtam routing service}{}{}{}{Development of service for computing optimal routes in road networks. I developed so far the following key parts of the system:
\begin{itemize}
  \item construction of road graph from different sources (Polish Map Format, Shapefile format and OSM) and and merging them into a single unit;
  \item preprocessing of Road Networks with Contraction Hierarchies;
  \item shortest path computation in road networks with turn costs;
\end{itemize}}
\cvline{tools}{\emph{Linux, C++, Boost, OMP, gcc, GNU make, Berkeley DB.}}

\cventry{}{Key developer of Wialon apps}{}{}{}{I implemented a few applications. Among them are Driving Logbook, Dashboard, Gurtam Maps, and iDriveSafe IQ. They are implemented using Wialon Hosting and Wialon Kit SDKs. Driving Logbook allows requesting reports/a report for a unit's trips with an opportunity of adjusting trip status and making user's notes. Dashboard provides an overview of fleet KPIs (key performance indicators) in an easy to read real-time user interface to enable instantaneous and informed decisions to be made at a glance. Gurtam Maps can be used in two ways: to search location and address by given coordinates and to search location and coordinates by given address or its part. iDriveSafe IQ is a comprehensive driving quality control system that allows evaluating drivers’ behavior and the way they treat their vehicles.}
\cvline{tools}{\emph{JavaScript.}}

\cventry{}{Key developer of \href{https://itunes.apple.com/ru/app/gps-tag/id901805399?mt=8}{GPS Tag Pro} and \href{https://itunes.apple.com/ru/app/gps-tag-orange/id766356081?mt=8}{GPS Tag Orange} iOS apps}{}{}{}{The application that helps determine your geographical position and track your movements. Full application development, bug-fixing, support of legacy code.}
\cvline{tools}{\emph{Objective C, SQLite.}}

\cventry{}{Developer of hosting.wialon.com}{}{}{}{Web-based GPS tracking software platform. Implementation of new features, bug-fixing, support of legacy code.}
\cvline{tools}{\emph{Linux, JavaScript, Tcl}}

\cventry{}{Key developer infrastructure for gps.velcom.by}{}{}{}{Personal GPS tracking web-based service. Development of the website and provisioning API, bug-fixing, support of legacy code. At the same time, I implemented a simple Python wrapper for Wialon Remote API.}
\cvline{tools}{\emph{Linux, JavaScript, Python 2, Tcl.}}

\section{Education}
\cventry{2009-2014}{Mathematician–software engineer degree}{BSUIR}{Minsk}{}{Graduated from \emph{Belarusian State University of Informatics and Radioelectronics} in \emph{2014}. Received \emph{mathematician--software engineer} degree.}

\section{Diploma project}
\cvline{title}{\emph{Service to provide distributed locks and storage of configurations}}
\cvline{description}{Development of a service for obtaining distributed locks using \emph{RAFT} consensus algorithm was the goal of the diploma project. The work was based on the article ``In Search of an Understandable Consensus Algorithm'' by Diego Ongaro and John Ousterhout presented at Stanford University. Project received a high grade and I was offered to continue education to receive second stage of higher education, as well as teach students at the ``Computer science'' department.}

\section{Personal projects}
\cventry{2016 - 2019}{Go developer}{}{}{}{Development a versatile agent that collects logs and forwards them to a cloud. Logs sources are collected from TCP and UDP connections, from file and cron job output. The following techniques and tricks were used: \href{https://github.com/omniti-labs/jlog}{JLog}, \href{https://en.wikipedia.org/wiki/Exponential_backoff}{exponential backoff}, \href{https://en.wikipedia.org/wiki/Circuit_breaker_design_pattern}{circuit breaker design pattern} and gracefully shutdown.}
\cvline{tools}{\emph{Linux, Go.}}

\cventry{2018 - 2019}{ClojureScript developer}{}{}{}{Development a web-based data visualization dashboard}
\cvline{tools}{\emph{Linux, ClojureScript, Leiningen.}}

\section{On the Web}
\cvlistitem{\url{http://github.com/achernetsky}}
\cvlistitem{\url{http://linkedin.com/in/achernetsky}}

\section{Languages}
\cvitemwithcomment{Spanish}{Beginner (A1)}{}
\cvitemwithcomment{English}{Intermediate (B1)}{}
\cvitemwithcomment{Russian}{Native}{}

\section{Tools used in personal/educational projects}
\cvcomputer{\textbf{Languages}}{C, Java, Scala, Scheme,\\ Octave, assembly language,\\ ClojureScript, Clojure, Go}{\textbf{Databases}}{MySQL, CouchDB}

\end{document}
